---
title: "Alcohol vs Seat choice"
author: "Tyler Hamblin"
date: "5 October 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??


$H_A$: The average number of drinks is significantly different between at least two rows. 

$H_0$: The location of seats is not related to the amount of drinks consumed. 

## Methods

```{r}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

This string of code changes all character variables into factor variables. This type of question needs a numerical variable (Alcohol) explained by a factor variable (Seat) which we can use a Num~Cat helper file from the CandP zip to guide us. 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


