---
title: "Alcohol vs Seat choice"
author: "Tyler Hamblin"
date: "5 October 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??


$H_A$: The average number of drinks is significantly different between at least two rows. 

$H_0$: The location of seats is not related to the amount of drinks consumed. 

## Methods

```{r}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

This string of code changes all character variables into factor variables. This type of question needs a numerical variable (Alcohol) explained by a factor variable (Seat) which we can use a Num~Cat helper file from the CandP zip to guide us. 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This fancy box plot displays the three categories for seating which are Front, Middle, and Back as they pertain to alcohol consumption. As it shows the people seated in the back have a median and range much greater than the upper quartile of the Front and Middle sections. Those sitting in the Middle and Front have medians and ranges much closer to 0 beverages consumed whereas the Back has a median of about 4 which an upper end of about 14. It is reasonable to assume that regardless of the outliers, the people seating in the back tend to statistically consume more alcohol than any of the other sections.

## Numerical Summarys 

## Inferential Tests

## Conclusions


